\documentclass[letterpaper]{article}

\usepackage{xltxtra}          % Use for unicode font support.
%\usepackage[T1]{fontenc}      % Correct font rendering.
%\usepackage[utf8]{inputenc}   % Correct font rendering.
%\usepackage{lmodern}          % Use fancy font.
%\usepackage[english]{babel}   % This document is in English.
\usepackage{tabularx}         % Use tables with spacing.
\usepackage{hyperref}         % Embed hyperlinks.
\usepackage{multicol}         % Produce multiple columns.
\usepackage{fancyhdr}         % Fancify your header
\setlength{\multicolsep}{0pt} % Don't add spacing after contact info.

%% Set custom page margins.
\usepackage[top=.9in,right=.5in,bottom=.4in,left=.5in]{geometry} %% SHRINK ME
%\usepackage[top=0.9in,right=.5in,bottom=.4in,left=.5in]{geometry}

%% Slightly decrease section header size.
\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}

%% Slightly increase section header spacing.
\usepackage{titlesec}
%                      {indentation}{above}{below}
\titlespacing{\section}{0pt}        {*3}   {*0.5}  %% SHRINK ME
%\titlespacing{\section}{0pt}        {*2}   {*0.3}

%% Decrease spacing between list items.
\usepackage{enumitem}
\setlist[itemize]{topsep=0.5em,partopsep=0em,parsep=0em,itemsep=0em}

%% Set normal font size; Set no page numbers; Set non-flush page ending
\normalsize
\pagestyle{fancy}

% Fancy headers
\setlength{\headheight}{18pt}
\renewcommand{\headrulewidth}{0.1pt}
\fancyhf{}

% Name
\lhead{\Large\textbf{Jean Michel Rouly}}

% Contact information
\rhead{
  \begin{tabularx}{12.5cm}{@{}rrrr@{}}
  {\fontspec{FontAwesome}} 571 218 7173 &
  {\fontspec{FontAwesome}} \href{mailto:michel@rouly.net}{michel@rouly.net} &
  {\fontspec{FontAwesome}} \href{michel.rouly.net}{michel.rouly.net} &
  {\fontspec{FontAwesome}} \href{http://github.com/jrouly}{github.com/jrouly}
  \end{tabularx}
}

\setlength{\headsep}{0.3cm}

%% Set up a custom itemize format for entry details
\newenvironment{details}
{\begin{itemize}}
{\end{itemize}}


\begin{document}

  %% Do not display section numbering
  \setcounter{secnumdepth}{0}

  %% Education
  \section{Education}

  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{Bachelors of Science in Computer Science} \emph{summa cum laude} & \textbf{Aug 2011 - May 2015} \\
    George Mason University, Fairfax, VA & \emph{Cumulative GPA: 3.95}
  \end{tabularx}

  \begin{details}
  \item Dean's List all semesters attended.
  \item Phi Kappa Phi academic honors society member.
  \item Honors College Extraordinary Service award recipient.
  \item Volgenau School of Engineering Distinguished Academic Achievement Award recipient.
  \item Volgenau School of Engineering Excellence in Undergraduate Writing Award recipient.
  \item University Scholars scholarship recipient (highest academic merit scholarship).
  \end{details}


%  %% Research
%  \section{Research Experience}
%
%  %% UA-ESE-REU
%  \noindent
%  \begin{tabularx}{\textwidth}{@{}X r@{}}
%    \textbf{Undergraduate Researcher} & \textbf{May 2014 - July 2014} \\
%    University of Alabama, Tuscaloosa, AL & \texttt{\href{reu.cs.ua.edu}{reu.cs.ua.edu}}
%  \end{tabularx}
%
%  \begin{details}
%  \item Analyzed graphical language IDEs for common attributes.
%  \item Contributed to Open Source modeling framework AToMPM.
%  \end{details}
%
%  %% AMALTHEA REU
%  \noindent
%  \begin{tabularx}{\textwidth}{@{}X r@{}}
%    \textbf{Undergraduate Researcher} & \textbf{May 2013 - July 2013} \\
%    Florida Institute of Technology, Melbourne, FL & \texttt{\href{amalthea-reu.org}{amalthea-reu.org}}
%  \end{tabularx}
%
%  \begin{details}
%  \item Constructed robust data mining framework in a cloud-computing environment.
%  \item Novel MapReduce implementation allowed scalability to Big Data problems.
%  \item Built using Apache Hadoop, Mahout, and Hive; deployed at scale on Amazon EC2 cloud.
%  \end{details}


  %% Experience
  \section{Work Experience}

  %% Rally Health
  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{Software Engineer} & \textbf{September 2015 - Present} \\
    Rally Health, Washington, D.C. & \texttt{\href{http://rallyhealth.com}{rallyhealth.com}}
  \end{tabularx}

  \begin{details}
  \item Developed large-scale search engine web application in Scala and Play.
  \item Utilized modern reactive and stream technology to serve RESTful web APIs.
  \item Served on-call rotations while managing production deploys to millions of consumers.
  \item Operated individually and in a team to design and implement solutions to frequently changing requirements.
  \end{details}

  %% GMU RTOC
  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{Lead Project Developer} & \textbf{Aug 2013 - January 2015} \\
    George Mason University Honors College, Fairfax, VA & \texttt{\href{http://honorscollege.gmu.edu/collegeresearch}{honorscollege.gmu.edu}}
  \end{tabularx}

  \begin{details}
  \item Developed crowd-sourced peer-review service for students pursuing research topics.
  \item Maintained multiple Linux web servers hosting online content for student access.
  \item Collaborated with research mentors to increase usability and value of services.
  \end{details}

  %% Harmonia
  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{Java Programming Consultant} & \textbf{June 2012 - June 2013} \\
    Harmonia Holdings Group, LLC, Tysons Corner, VA & \texttt{\href{harmonia.com}{harmonia.com}}
  \end{tabularx}

  \begin{details}
  \item Created components of a Learning Classifier engine.
  \item Collaborated with project manager on high level systems architecture design.
  \item Spearheaded design and implementation for complex graphical user interfaces, all to-specification.
  \end{details}

%  %% TIC
%  \noindent
%  \begin{tabularx}{\textwidth}{@{}X r@{}}
%    \textbf{TIC Summer Camp,} McLean, VA & \textbf{June 2011 - August 2011} \\
%    \emph{Programming Counselor} & \emph{Java, LOGO, Instruction}
%  \end{tabularx}
%
%  \begin{details}
%  \item Worked closely and autonomously with small groups of students.
%  \item Instructed students in introductory game design using LOGO.
%  \item Introduced students to programming in Java.
%  \item Compiled formal quarterly reports on student progress and behavior.
%  \end{details}


  %% Leadership Experience
  \section{Leadership Experience}
  \noindent
  \begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{President and Co-Founder} & \textbf{August 2013 - May 2014} \\
    Student-Run Computing and Technology (SRCT), Fairfax, VA & \texttt{\href{srct.gmu.edu}{srct.gmu.edu}}
  \end{tabularx}

  \begin{details}
  \item Managed and deployed Open Source projects to benefit the campus community.
  \item Maintained multiple Linux web servers hosting software services.
  \item Coordinated and led large-scale community outreach events.
  \end{details}


  %% Publications
  \section{Publications}
  \noindent
  \begin{details}
  \item Rouly, J. M., Rangwala, H., and Johri, A. (2015, July). What Are We
  Teaching?: Automated Evaluation of CS Curricula Content Using Topic
  Modeling. In \emph{Proceedings of the eleventh annual International
  Conference on International Computing Education Research} (pp. 189-197). ACM.

  \item Rouly, J.M, Orbeck, J. D., and Syriani, E.
  Usability and Suitability Survey of Features in Visual IDES for
  Non-Programmers. In \emph{Proceedings of the 5th Workshop on Evaluation
  and Usability of Programming Languages and Tools, PLATEAU '14}, pages
  31–42, New York, NY, USA, 2014. ACM.

  \item Rose, D. M., Rouly, J. M., Haber, R., Mijatovic, N., \& Peter, A.
  M. (2013, December). Parallel Hierarchical Affinity Propagation with
  MapReduce. In \emph{Cloud Computing Technology and Science (CloudCom),
  2013 IEEE 5th International Conference on} (Vol. 2, pp. 13-18). IEEE.
  \end{details}


  %% Skills
  \section{Technical Skills}
%  \noindent
%  \begin{tabularx}{\textwidth}{@{}X r@{}}
%    \textbf{Languages \& Tools} & \textbf{Operating Systems} \\
%    Scala, Python, C, Java, SQL, Javascript, HTML, CSS, ElasticSearch, R, PHP, Django, Flask, Git, SVN
%    &
%    Linux/UNIX; Windows
%  \end{tabularx}

    \noindent\textbf{Languages \& Tools} \\
    Scala, Akka, Play, ElasticSearch, Python, C, Java, SQL, Javascript, HTML, CSS, R, PHP, Django, Flask, Git, SVN \\

    \noindent\textbf{Operating Systems} \\
    Linux/UNIX, Windows, Mac OSX


  %% References
%  \section{References}
%  \noindent Available on request.


\end{document}
